### 2012-06-18 inst/examples/value_of_information.Rmd
new runs

``` {r } 
simulatereps <- function(opt, true_g, true_m, true_i){
  z_g <- function() rlnorm(1,  0, true_g) 
  z_m <- function() rlnorm(1,  0, true_m) 
  z_i <- function() rlnorm(1,  0, true_i)

@@

  list(sims = sims, opt = opt, true_stochasticity = c(true_g, true_m, true_i))
}
````

Corner cases

``` {r }
base <- simulatereps(det, 0, 0, 0)
reckless <- simulatereps(det, .2, .2, .2)
````

``` {r }
full <- simulatereps(gmi, .2, .2, .2)
cautious <- simulatereps(gmi, 0, 0, 0)
````

``` {r tidy}
sims <- list(base = base$sims, full = full$sims, reckless=reckless$sims, cautious=cautious$sims)
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
````

@@

``` {r  fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario"}
p1 <- ggplot(dt) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
````

``` {r fig.cap="The profits made in each time interval of a single replicate, by scenario"}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)

@@

``` {r fig.cap="the distribution of profits by scenario"}
profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
````

>>>>

``` {r simfn} 
simulatereps <- function(opt, true_g, true_m, true_i){
  z_g <- function() rlnorm(1,  0, true_g) 
  z_m <- function() rlnorm(1,  0, true_m) 
  z_i <- function() rlnorm(1,  0, true_i)

@@

#  list(sims = sims, opt = opt, true_stochasticity = c(true_g, true_m, true_i))
  sims
}
````

All cases

``` {r runallsims} 
policyfn <- list(det=det, g=g, m=m, i=i, gm=gm, gi=gi, gmi=gmi)
noise <- list(s0=c(0,0,0), sg=c(.2, 0, 0), sm=c(0, .2, 0), si=c(0,0,.2), sgm=c(.2, .2, 0), sgi=c(.2, 0, .2), sgmi=c(.2, .2, .2)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3]
  })
})
````

``` {r tidyall}
sims <- unlist(allcases, recursive=FALSE)
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
````

@@

``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario"}
p1 <- ggplot(dt) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
````

``` {r profits_time, fig.cap="The profits made in each time interval of a single replicate, by scenario"}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, profit))  + facet_wrap(~uncertainty)

@@

``` {r profits, fig.cap="the distribution of profits by scenario"}
profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
````
